---
title: "GR5291-final"
author: "Biying Deng(bd2532)"
date: "10/1/2019"
output: html_document
---

```{r}
library(ggplot2)
library(tidytext)
library(dplyr)
airbb<-read.csv("~/Desktop/GR5291 Advanced ML/Final project/data/AB_NYC_2019.csv")

summary(airbb)

```

Data cleaning 

1.convert empty data into NA
```{r}


#function to convert
empty_as_na<-function(x){
  if("factor" %in% class(x)) x <-as.character(x)
  ifelse(as.character(x) !="",x,NA)
}
airbb<-airbb %>% mutate_each(funs(empty_as_na))

#get total num of na in all columns
sapply(airbb,function(x) sum(is.na(x)))

```
"last_review" is date, there are no reivews for the listing, date will not exist.

when "number_of_review" is 0, we can follow our logic that the listing won't have any review and therefore will have "review_per_month" 0.Then we can replace NA in "review_per_month" with 0

# drop unimportant variabes: id, host_name

```{r}
airbb<-airbb[,-c(1,4)]
```

# replace NA in "review_per_month" with 0

```{r}
airbb$reviews_per_month[is.na(airbb$reviews_per_month)==T]<-0

#check replacement success or not
sum(is.na(airbb$reviews_per_month))
```

# replace NA name with None
```{r}
airbb$name[is.na(airbb$name)==T]<-"None"

```

```{r}
airbb$host_id<-as.character(airbb$host_id)
```



# Explore neighborhood group and neighborhood
```{r}
unique(airbb$neighbourhood_group)
length(unique(airbb$neighbourhood))

# For each neighborhood_group, number of distinct neighborhood under each neighborhood_group
airbb %>% group_by(neighbourhood_group) %>% summarise(num=n_distinct(neighbourhood))

```

There are three major neighborhoods in New York City: Bronx, Brooklyn, Queens, Staten Island.

```{r}
 sort_num_listing<-airbb %>% group_by(host_id) %>% summarise(listing=n()) %>% arrange(desc(listing)) %>% head(10)

ggplot(sort_num_listing,aes(y=listing,y=fill=factor(host_id))) + geom_bar()

airbb %>% filter(host_id=="219517861")


airbb %>% select(name,host_id) %>% unnest_tokens(word,name) %>% anti_join(stop_words) %>% count(word,sort = T) 
```


